# Shiny

```{r setup, include=FALSE}
WORDS_TO_IGNORE <- c("DataCamp")
source("knitr-options.R")
source("spelling-check.R")
```

## Example

You see my Shiny App for creating pixel art models.

```{r, eval=FALSE}
# Installation
remotes::install_github("privefl/pixelart")

# Run Shiny App
pixelart::run_pixelart()
```

## DataCamp course

~~Let us use [this free DataCamp course](https://noamross.github.io/datacamp-sexual-assault/) to learn the basics of Shiny.~~

We won't use DataCamp for this course anymore because
<blockquote class="twitter-tweet" data-lang="en" align="center"><p lang="en" dir="ltr">Please don&#39;t take or pay for my <a href="https://twitter.com/DataCamp?ref_src=twsrc%5Etfw">@DataCamp</a> course. The company let its executive off the hook for sexual misconduct.  We can&#39;t change behavior without incentives, and for companies those incentives are financial. <a href="https://t.co/UlTFXdoI6B">https://t.co/UlTFXdoI6B</a> <a href="https://twitter.com/hashtag/python?src=hash&amp;ref_src=twsrc%5Etfw">#python</a> <a href="https://twitter.com/hashtag/rstats?src=hash&amp;ref_src=twsrc%5Etfw">#rstats</a> <a href="https://twitter.com/hashtag/datascience?src=hash&amp;ref_src=twsrc%5Etfw">#datascience</a> <a href="https://twitter.com/hashtag/MeToo?src=hash&amp;ref_src=twsrc%5Etfw">#MeToo</a></p>&mdash; Noam Ross (@noamross) <a href="https://twitter.com/noamross/status/1116667602741485571?ref_src=twsrc%5Etfw">12 avril 2019</a></blockquote>
<script async src="https://platform.twitter.com/widgets.js" charset="utf-8"></script>


## Other resources

- [Mastering Shiny](https://mastering-shiny.org/).

- [Shiny website](http://shiny.rstudio.com/)

- [Shiny gallery](https://shiny.rstudio.com/gallery/)

- [Shiny themes](http://rstudio.github.io/shinythemes/)

- [Shiny tutorials](http://shiny.rstudio.com/tutorial/)

- [Shiny dashboards](http://rstudio.github.io/shinydashboard/)

- [Shiny widgets](https://dreamrs.github.io/shinyWidgets/index.html)

- [Advanced Shiny tips](https://deanattali.com/blog/advanced-shiny-tips/)

- [JavaScript operations in Shiny](https://deanattali.com/shinyjs/)

- [Getting Started with Shiny](https://ourcodingclub.github.io/2017/03/07/shiny.html)

- [A gradual introduction to Shiny](https://laderast.github.io/gradual_shiny/)


