# Shiny

```{r setup, include=FALSE}
WORDS_TO_IGNORE <- c("DataCamp")
source("knitr-options.R")
source("spelling-check.R")
```

## Example

You see my Shiny App for creating pixel art models.

```{r, eval=FALSE}
# Installation
remotes::install_github("privefl/pixelart")

# Run Shiny App
pixelart::run_pixelart()
```

## DataCamp course

~~Let us use [this free DataCamp course](https://noamross.github.io/datacamp-sexual-assault/) to learn the basics of Shiny.~~

We won't use DataCamp for this course anymore. See why [here](https://t.co/UlTFXdoI6B).


## Other resources

- [Mastering Shiny](https://mastering-shiny.org/)

- [Shiny website](http://shiny.rstudio.com/)

- [Shiny gallery](https://shiny.rstudio.com/gallery/)

- [Shiny themes](http://rstudio.github.io/shinythemes/)

- [Shiny tutorials](http://shiny.rstudio.com/tutorial/)

- [Shiny dashboards](http://rstudio.github.io/shinydashboard/)

- [Shiny widgets](https://dreamrs.github.io/shinyWidgets/index.html)

- [Advanced Shiny tips](https://deanattali.com/blog/advanced-shiny-tips/)

- [JavaScript operations in Shiny](https://deanattali.com/shinyjs/)

- [Getting Started with Shiny](https://ourcodingclub.github.io/2017/03/07/shiny.html)

- [A gradual introduction to Shiny](https://laderast.github.io/gradual_shiny/)


